---
title: "Styleguide"
author: "Unity Tambellini-Smth"
date: "2024-09-25"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

In this guide we will show you the basics of cleaning and styling a chart once you have created the basic skeleton.

```{r}
basic_plot <- iris |> ggplot(aes(x = Sepal.Length, y = Sepal.Width))+
  geom_point()
```


# Labeling 
```{r}
basic_plot <- basic_plot +
  labs(x = "this is how you label x", y = "this is how you label y", title = "An Example Chart")
```

# Fonts

At TSL, charts are to be created using 'Palatino Linotype' font. This font does not come with R, in order to download and use it:

1. Uncomment and run the following code block, answer any propts that appear in the console
```{r, echo=FALSE}
#install.packages('extrafont')
#library(extrafont)
#font_import(paths = c('Palatino Linotype'))
```

Congrats! You now have the font.

2. To set the font of a chart use the theme() function
```{r}
basic_plot <- basic_plot+
  #LINE TO CHANGE FONT
  theme(text=element_text(
      family="Palatino"), #font style
      )

basic_plot
```

# Colors

```{r}
#
```


# Manipulating Axes